\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-09 coqimpl.tex
Fixing section Extensible Inductive Type.

\textbf{``Extensible'' Inductive Type and Defining Recursor/Eliminator.}
We support extensible inductive types in Coq mentioned in
\ref{chg:extensible-inductive-type}, but we will not be aiming at the
research of its formal semantic.\footnote{Because to give a satisfactory
formal definition and semantic for extensible inductive type is not
something this paper aims at, and obviously requires more theoretical
research effort}
%\YZ{I do consider that your plugin supports extensible inductive types. It's just that they are implemented as a plugin, rather than in the Coq core.}\EDJreply{I rephrased it. It is more like I don't think this is really the final form of extensible inductive type that everyone is happy about}

@@

Let's look at the exemplar \cref{fig:plugin-example2}, the example of
"subst" on STLC. When we define the extensible inductive type "tm", all
the following fields (e.g., "subst_internal.tm_var") can only know "tm"
is a type (of "Set") and there are at least two constructors for it,
just like what we declare in ``the abstracted interface''---the compiled
module type "STLC_Interface". We cannot export
%\YZ{export or put?}\EDJreply{Ok.
%I just figure out how my wording is confusing. put is absolutely correct
%but by put I want to mean ``export''. I think I use ``export'' in
%several places...}
the eliminator of the inductive type "tm" to "STLC_Interface".
Otherwise all the subsequent fields (e.g. "subst_internal.tm_var" and
the corresponding "tm_var_411") would not be able to be inherited to the
context where "tm" is extended with a third constructor, \textbf{since
the mere existence of the recursor will assert that there are only two
constructors} in "STLC_bool", not \textbf{extensible} at all!

However, we later still need the concrete eliminator on "tm" for doing
exhaustiveness checking (as in \ref{chg:extensible-inductive-type}),
thus we will store the corresponding info somewhere.  Here we show one
exemplar extraction of the eliminator to \mintinline{Coq}{Set} as module
"tm_rec_type". This concrete eliminator will be used by our "FRecursor".
For example, in \cref{fig:plugin-example2}, "FRecursor" command will
feed Coq a module "do_tc" for doing type-checking with specified
handlers (e.g. "neg_handler") during compilation---what it does is
basically
assert the existence of the recursor and apply to see if handlers can
pass the type checking by Coq.\YZ{
  Sounds like we can still claim the plugin is doing type checking.
  It's just that the checking is done by generating some Coq code and
  then having Coq check it.
}\EDJreply{Yes! If my phrasing doesn't make things clear (i.e. our plugin is doing typechecking),
feel free to change the phrasing for me}
Note that, at this point of the example,
"FRecursor" will only do type check. The compilation of "FRecursor" into
a component of the compiled module only happens when closing the whole
family, by inserting the following into the compiled module: 
\begin{minted}{Coq}
Definition subst := tm_rec (λ _ ⇒ id → tm → tm) subst_internal.tm_var ...
\end{minted}
where "tm_rec" and "tm" are the corresponding recursor and
the (vanilla) inductive type in that compiled module. Thus a "FRecursor"
field is unlike other fields, even though it is exposed as a plain
function for the succeeding fields in the programming interface.

The plugin actually realizes the "Extend FInductive" via overriding---%
when extending an inductive type $A$ with new constructor $c$, our
plugin will generate a new (syntactic) inductive definition $A'$ with
this new $c$ on the fly and feed it to Coq. But we must be careful on
the exposing data in the family type (the compiled module type) for the
succeeding field. In other words, we must be careful on the interface
(context) based on which the succeeding fields are defined.

Importantly, the recursor field (e.g. "subst") is not actually
inheritable, because it is not compiled like any other fields.
Recall how other fields are compiled into reusable pieces of
(parametrized) modules; a recursor field is not compiled like that.
For all the children family, we have to reconstruct and override the
"FRecursor" field with a ``new'' recursor using (maybe the same) handler
family.  This is affordable since each aggregated recursor handler
doesn't need to be rechecked---look at "STLC_bool.neg_handler", there
are only  new handlers for "tm_true" and the handlers (mundane fields)
from the parent "B.subst_internal.tm_var" have already been type-checked
and inherited (since they only rely on ``the abstracted interface''
module "STLC_Interface"). 
Thanks to family inheritance, their corresponding compiled module from the parents---for example, 
the module "tm_var_411"---doesn't require another type-check and is
re-used during the type-checking and compilation of "STLC_bool.subst".
For example, for the new "subst", when compiling family "STLC_bool" into
a module, at the appropriate place our plugin will insert
\begin{minted}{Coq}
Definition subst := tm_rec (λ _ ⇒ id → tm → tm) subst_internal.tm_var ...
\end{minted}
where "tm_rec" and "tm" are the corresponding recursor and the (vanilla
but extended and modified) inductive type in that compiled module.\YZ{Where is this "tm" inductive type in figure 6?} Note
that, even though "tm_rec" and "tm" has the same name as before, they
are in the newly-compiled module so they refer to totally different
things.

Of course, in the implementation, our plugin will ``inherit'' the
recursor "neg" in the surface,
but what the plugin actually does is doing a second exhaustiveness
checking in children family like mentioned above, with the ``same'' motive and the ``same'' handler family.
%\YZ{A source of confusion in this section is that the reader often has to guess who performs the actions: is it the programmer or the Coq plugin?}\EDJreply{Good idea. Let me reorgnaize this section to ``first programming interface'', then ``plugin implementation''}

@@

% explain ftheorem wrapping this complicated recursor
This design of decoupling of the case handlers and exhaustiveness
checking handles the semantic well, however, it brings a lot of
boilerplate code---we need to create an extra (handler) family, manually
specifying the type of each case handlers, and then using "FRecursor" to
``tie the knot'' and construct a recursor field from the handlers.  
We thus provide a command "FTheorem" to avoid these boilerplate in programming interface when using tactic programming. 
This command (1) can avoid specifying the handlers family and the type of each case handlers when writing induction like above, (2) invoke
proof interaction mode and thus allow tactic programming, (3) and is also open to extension like "FRecursor". We expect this "FTheorem" to be used in theorem proving but not general programming.

To summarize, (1) to make each recursor
handler inheritable, we need to seal an abstraction around the inductive
type (e.g., module "b_3"); but to construct a recursor (and carry out the
exhaustiveness checking), we need to break this abstraction and see the
concrete definition of the inductive type (e.g., module "b_rec_12"). Our
meta-theory need to handle these two seemingly contradicting ideas
simultaneously when solving \ref{chg:extensible-inductive-type}.
(2) \ref{chg:extensible-inductive-type} is also resolved by this
\textit{decoupling} of the syntax of implementation of recursor handlers
and exhaustiveness checking. The former is handled by family inheritance
and thus avoiding the boilerplate code; and the non-inheritance of the
compiled recursor ensures the exhaustiveness checking happens for every
recursor.

@@

However, "FRecursor" provides barely enough functionality for
manipulating our(extensible) inductive type, and it is far from
satisfactory to be a legitimate programming interface. (1) We do not yet
have any computational information using this "FRecursor" until its
compilation into module, i.e. we cannot do computation with it during
the construction of the family using the current compilation strategy.
(2) The necessary tactic like "discriminate" and "injection" is not
applicable on (extensible) inductive type.

% \textit{Generating Scheme for Propositional Computation Axiom for FRecursor}.

Thus we support "FScheme" to remedy problem (1): our plugin can automatically generate(postulate) the computational ``axiom'' for the specified  into the family and prove them during compilation into modules. However, it is only introducing computational information \textbf{propositionally} but not judgementally, and we might need the help of rewriting tactic on these computational ``axiom'' to justify the computation.

>>>>

\textbf{``Extensible'' Inductive Type and Defining Recursor/Eliminator.}
We support extensible inductive types in Coq mentioned in
\ref{chg:extensible-inductive-type}.
% \footnote{Because to give a satisfactory
% formal definition and semantic for extensible inductive type is not
% something this paper aims at, and obviously requires more theoretical
% research effort}
%\YZ{I do consider that your plugin supports extensible inductive types. It's just that they are implemented as a plugin, rather than in the Coq core.}\EDJreply{I rephrased it. It is more like I don't think this is really the final form of extensible inductive type that everyone is happy about}

@@

We illustrate the usage and plugin implementation of inductive type and reasoning in the exemplar \cref{fig:plugin-example2}, the example of
"subst" on STLC. When we define the extensible inductive type "tm", all
the following fields (e.g., "subst_internal.tm_var") can only know "tm"
is a type (of "Set") and there are at least two constructors for it,
just like what we declare in ``the abstracted interface''---the compiled
module type "STLC_Interface". However, we will not export
%\YZ{export or put?}\EDJreply{Ok.
%I just figure out how my wording is confusing. put is absolutely correct
%but by put I want to mean ``export''. I think I use ``export'' in
%several places...}
the eliminator of the inductive type "tm" to "STLC_Interface", \textbf{since
the mere existence of the eliminator will assert that there are only two
constructors} in "tm", lead to an \textbf{non-extensible} "tm"! Thus the "STLC_Interface" will only include the ``constructor'' themselves in the form of parameter function. Doing so, all the subsequent fields (e.g. "subst_internal.tm_var" and the corresponding compiled "tm_var_handle") can be inherited to the
context where "tm" is extended with new constructors without re-typechecking (re-compilation).

To construct recursive function on a given inductive type, we use "FRecursion". "FRecursion" is a syntax sugar with (1) a normal family that includes all the case handling as field members, and (2) a step of doing type-checking and exhaustiveness checking (as in \ref{chg:extensible-inductive-type}). By considering all the case handling gathered in a family, the extension of the case handling can be simplified as the extension of the family. In our example, the resulting handler family is "subst_internal_410". While to achieve type-checking, we require the signature of eliminator about "tm" to be exposed. Here we show one
exemplar extraction of the eliminator to \mintinline{Coq}{Set} as module
"tm_rec_type". This concrete eliminator will be used by our "FRecursion".
For example, in \cref{fig:plugin-example2}, after closing an "FRecursion" block, our plugin will feed Coq the module "do_tc" for doing type-checking with specified
handlers (e.g. "subst_internal_410") during compilation---what it does is
basically
assert the existence of the recursor and apply to see if handlers can
pass the type checking by Coq.\YZ{
  Sounds like we can still claim the plugin is doing type checking.
  It's just that the checking is done by generating some Coq code and
  then having Coq check it.
}\EDJreply{Yes! If my phrasing doesn't make things clear (i.e. our plugin is doing typechecking),
feel free to change the phrasing for me}

% Note that, at this point of the example,
% "FRecursion" will only do type check via "do_tc". 
% The compilation of "FRecursor"  only happens when closing the whole
% family, by including "subst_18". 
% However, notice the context (parameter) of the "subst_18": it is "ctx_subst_113", where the concrete inductive type is exposed in the context, instead of "STLC_Interface". This concrete exposition makes "__internal_tm_rec" accessible, but also makes "subst_18" non-inheritable when "tm" is extended. Thus in every children family, modules like "subst_18" needs to be regenerated.
% Thus a "FRecursion" field is unlike normal fields, 
% even though it is exposed as a plain
% function for the succeeding fields in the programming interface.

Note that, the "FRecursion" field (e.g. "subst") is not actually
inheritable, because it is not compiled like any other fields.
Recall how other fields are compiled into reusable pieces of
(parametrized) modules; a recursor field is not compiled like that.

In our example "STLC", when the "FRecursion" block is closed, it will only do type check via "do_tc".  The compilation of "FRecursion"  
only happens when closing the top-level
family "STLC", by generating "subst_18" on-the-fly and assembly it into "module STLC". .
However, notice the context (parameter) of the "subst_18": it is "ctx_subst_113", where the concrete inductive type is exposed in the context, instead of "STLC_Interface". This concrete exposition makes "__internal_tm_rec" accessible, but also makes "subst_18" non-inheritable when "tm" is extended.
Thus, for all the children family, we have to regenerate module and replace the
module with the ``new'' recursor using ``the same'' handler
family (e.g. "Module subst_242", whose context "self__STLC_bool" is also different from that of the parent).

This is affordable since each aggregated recursor handler
doesn't need to be rechecked: look at surface syntax, the user only need to handle the new constructors like "tm_true" in "STLC_bool.subst"; during compilation,"Module subst_internal_248" will directly include the old handlers 
from the parent (e.g. "STLC.subst_internal.tm_var") that have already been type-checked (since they only rely on ``the abstracted interface''
module "STLC_Interface" and thus well-typed). 
Thanks to family inheritance, their corresponding compiled module from the parents---for example, 
the module "tm_var_handler"---doesn't require another type-check and is
re-used during the type-checking and compilation of "STLC_bool.subst".

Of course, in the implementation, these details are all hidden and when the user ``inherit'' the recursor "subst" in the surface syntax,
our plugin actually will actually do a second exhaustiveness
checking in children family mentioned above, with the ``same'' motive and the ``same'' handler family.
%\YZ{A source of confusion in this section is that the reader often has to guess who performs the actions: is it the programmer or the Coq plugin?}\EDJreply{Good idea. Let me reorgnaize this section to ``first programming interface'', then ``plugin implementation''}

The plugin realizes the "Extend FInductive" via overriding---%
when extending an inductive type $A$ with new constructor $c$, our
plugin will generate a new (syntactic) inductive definition $A'$ with
this new $c$ on the fly and feed it to Coq. But we must be careful on
the exposing data in the family type (the compiled module type) for the
succeeding field. In other words, we must be careful on the interface
(context) based on which the succeeding fields are defined.

@@

% explain ftheorem wrapping this complicated recursor
% This design of decoupling of the case handlers and exhaustiveness
% checking handles the semantic well, however, it brings a lot of
% boilerplate code---we need to create an extra (handler) family, manually
% specifying the type of each case handlers, and then using "FRecursor" to
% ``tie the knot'' and construct a recursor field from the handlers.

For theorem proving, we provide a command "FInductive" that is doing similarly as "FRecursion" in programming interface but using tactic programming. Like "FRecursion", "FInduction" can handle newly added constructor in the children family as well.

% This command (1) can avoid specifying the handlers family and the type of each case handlers when writing induction like above, (2) invoke
% proof interaction mode and thus allow tactic programming, (3) and is also open to extension like "FRecursor". We expect this "FTheorem" to be used in theorem proving but not general programming.

To summarize, (1) to make each recursor
handler inheritable, we need to seal an abstraction around the inductive
type (e.g., module "STLC_Interface"); but to construct a recursor (and carry out the
exhaustiveness checking), we need to break this abstraction and see the
concrete definition of the inductive type (e.g., module "tm_rec_type"). Our
meta-theory need to handle these two seemingly contradicting ideas
simultaneously when solving \ref{chg:extensible-inductive-type}.
(2) \ref{chg:extensible-inductive-type} is also resolved by this
\textit{decoupling} of the syntax of implementation of recursor handlers
and exhaustiveness checking under the syntax sugar. 
The former is handled by family inheritance
and thus avoiding the boilerplate code; and the non-inheritance of the
compiled recursor ensures the exhaustiveness checking happens for every
recursor.

@@

However, "FRecursor" provides barely enough functionality for
manipulating our(extensible) inductive type, and it is far from
satisfactory to be a legitimate programming interface. (1) We do not yet
have any computational information using this "FRecursion" until its
compilation into module, i.e. we cannot do computation with "subst" during
the construction of the family using the current compilation strategy.
(2) The necessary tactic like "discriminate" and "injection" is not
applicable on (extensible) inductive type.

\textit{Generating Scheme for Propositional Computation Axiom for FRecursor}. Thus we support "FScheme" to remedy problem (1): our plugin can automatically generate(postulate) the computational ``axiom'' for the specified  into the family and prove them during compilation into modules. However, it is only introducing computational information \textbf{propositionally} but not judgementally, and we might need the help of rewriting tactic on these computational ``axiom'' to justify the computation.

### 2022-10-09 ext-ind-type-compilation-example.tex
Fixing section Extensible Inductive Type.

\begin{lstlisting}
Family STLC.[@\tanc{Ext-Ind-Cmp-start}@]
 FInductive tm : Set := tm_var : [@\dadada@]
 (* [@\dadada@] other constructors *) 
 FScheme tm_prec PRecT about self__STLC.tm.
 FScheme Comp about self__STLC.tm_prec.
 (* Generate Partial Recursor 
    and the computational axiom for tm *)
 Family subst_internal. 
  Final Field tm_var : [@\dadada@]
  := fun s x t => 
    if (eqb x s) then t else (tm_var s).
  (* [@\dadada@] other cases *)
 EndFamily.
 FRecursor subst 
  about tm 
  motive (fun _ => id → tm → tm)
  using subst_internal
  by _rec.
(* Field test := (subst (tm_var 0) 0 (tm_var 0)). *)
(* [@\dadada@] other things in STLC *)
EndFamily.
Family STLC_bool extends STLC.
(* [@\dadada@] *)
 Extend FInductive tm : Set :=
  | tm_true : tm [@\dadada@]
  (* [@\dadada@] other new constructors *)
 Extend Family subst_internal.
  Final Field tm_true : [@\dadada@]
   := fun x t => tm_true.
  (* [@\dadada@] other extended cases *)
 EndFamily. 
 Inherits subst.
(* [@\dadada@] other things in STLC_Bool *)
EndFamily.[@\tanc{Ext-Ind-Cmp-end}@]
\end{lstlisting}

\makeline[0pt]{Ext-Ind-Cmp-start}{Ext-Ind-Cmp-end}[codecomment-color!50]
\vspace{-3pt}

@@

\begin{lstlisting}
(* Compilation Of the above *) [@\tanc{Cmp-Result0-start}@]
Module Type STLC_Interface. 
  Parameter (tm : Set).
  Parameter (tm_var : id → tm).
  Parameter (tm_abs : id → tm → tm).
  (* [@\dadada@] and all the fields for inductive type [@\dadada@] *)
End STLC_Interface.
(* Collect eliminator to Set for tm *)
Module tm_rec_type (STLC: STLC_Interface).
  Definition __recursor_type_tm_rec :=
    forall P : STLC.tm -> Set,
    (forall n : id, P (STLC.tm_var n)) ->
    (forall (n : id) (i : STLC.tm),
    P i -> P (STLC.tm_abs n i)) ->
    [@\dadada@] -> forall i : STLC.tm, P i.
End tm_rec_type. [@\tanc{Cmp-Result0-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
(* Compiled Field STLC.subst_internal.tm_var *) [@\tanc{Cmp-Result-start}@]
Module tm_var_handle (self__STLC: STLC_Interface)
    (self__subst_internal: EmptySig_84).
  Definition tm_var :
    forall (s : ident) (x : ident) 
    (t : self__STLC.tm), self__STLC.tm :=
    fun s x t => if eqb x s
       then t else self__STLC.tm_var s.
End tm_var_handle. (* [@\dadada@] and more *)
(* Assembling STLC.subst_internal when compilation *)
Module subst_internal_410 (STLC: STLC_Interface). 
 Module subst_internal.
 Include tm_var_handle STLC. Include tm_abs_handle STLC.
 Include tm_app_handle STLC. Include tm_unit_handle STLC.
 End subst_internal.
End subst_internal_410.
(* Intermediate Module solely for type checking *)
Module do_tc (STLC: STLC_Interface).
  Include tm_rec_type STLC.
  Parameter (recursor_for_type_checking 
    : __recursor_type_tm_rec).
  Definition term_for_type_checking :=
    recursor_for_type_checking 
      (fun _  ⇒ id → STLC.tm → STLC.tm)
      subst_internal_410.tm_var [@\dadada@] .
End do_tc.
(* Ctx that expose concrete inductive type *)
Module Type ctx_subst_113.
Inductive __internal_tm : Set := [@\dadada@] 
Include subst_internal_410. (* [@\dadada@] and more inclusion *)
End ctx_subst_113.
(* Compilation of recursor, not reusable
    when inductive type extended due to the ctx *)
Module subst_128 (self__STLC: ctx_subst_113).
Include __motive_of_subst_107 self__STLC.
Definition subst :=
  self__STLC.__internal_tm_rec __motiveTsubst
	self__STLC.subst_internal.tm_var [@\dadada@] .
End subst_128.
(* Assembling the whole STLC *)
Module STLC.
Include tm_5. Include tm_prec_72. Include tm_prectm_81.
Include subst_internal_410. Include subst_128.
End v_129.
(* Assembling STLC_bool.subst_internal via reusing 
    most of the former compilation results *)
Module subst_internal_248 (STLC_bool: STLC_Interface).
Include tm_true_197 STLC_bool. Include [@\dadada@]
(* The Reused Compilation result *)
Include tm_var_handle STLC_bool. Include [@\dadada@]
End v_248. [@\tanc{Cmp-Result-end}@]
\end{lstlisting}

>>>>

\begin{lstlisting}
Family STLC.[@\tanc{Ext-Ind-Cmp-start}@]
 FInductive tm : Set := tm_var : [@\dadada@]
 (* [@\dadada@] other constructors *) 
 FScheme tm_prec PRecT about self__STLC.tm.
 FScheme Comp about self__STLC.tm_prec.
 (* Generate Partial Recursor 
    and the computational axiom for tm *)
 FRecursion subst on tm 
 motive (fun _ => id → tm → tm). 
  Case tm_var := fun s x t => 
    if (eqb x s) then t else (tm_var s).
  (* [@\dadada@] other cases *)
 End subst.
(* Field test := (subst (tm_var 0) 0 (tm_var 0)). *)
(* [@\dadada@] other things in STLC *)
EndFamily.
Family STLC_bool extends STLC.
 Extend FInductive tm : Set :=
  | tm_true : tm [@\dadada@]
  (* [@\dadada@] other new constructors *)
 FRecursion subst.
  Case tm_true := fun x t => tm_true.
  (* [@\dadada@] other extended cases *)
 End subst. 
 Inherits subst.
(* [@\dadada@] other things in STLC_Bool *)
EndFamily.
[@\tanc{Ext-Ind-Cmp-end}@]
\end{lstlisting}

\makeline[0pt]{Ext-Ind-Cmp-start}{Ext-Ind-Cmp-end}[codecomment-color!50]
% \vspace{-3pt}

@@

\begin{lstlisting}
(* Compilation Of the above *) [@\tanc{Cmp-Result0-start}@]
Module Type STLC_Interface. 
  Parameter (tm : Set).
  Parameter (tm_var : id → tm).
  Parameter (tm_abs : id → tm → tm).
  (* [@\dadada@] and all the fields for inductive type [@\dadada@] *)
End STLC_Interface.
(* Collect eliminator to Set for tm *)
Module tm_rec_type (STLC: STLC_Interface).
  Definition __recursor_type_tm_rec :=
    forall P : STLC.tm -> Set,
    (forall n : id, P (STLC.tm_var n)) ->
    (forall (n : id) (i : STLC.tm),
    P i -> P (STLC.tm_abs n i)) ->
    [@\dadada@] -> forall i : STLC.tm, P i.
End tm_rec_type.  
Module tm_prec_72 (self__STLC: STLC_Interface).
Definition tm_prec :
  forall i : tm, forall P : tm -> Type,
  (forall n, option (P (tm_var n))) ->
  [@\dadada@], option (P __i) :=
End tm_prec_72. 
Module Type substtm_139 (self__STLC: [@\dadada@]).
Parameter
  (subst_on_tm_unit :
	 eq (self__STLC.subst (self__STLC.tm_unit))
       self__STLC.subst_internal.tm_unit).
(* [@\dadada@] subst equality on other constructors *)
End substtm_139. 
[@\tanc{Cmp-Result0-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
(* Compiled Field STLC.subst_internal.tm_var *) [@\tanc{Cmp-Result-start}@]
Module tm_var_handle (self__STLC: STLC_Interface)
    (self__subst_internal: EmptySig_84).
  Definition tm_var :
    forall (s : ident) (x : ident) 
    (t : self__STLC.tm), self__STLC.tm :=
    fun s x t => if eqb x s
       then t else self__STLC.tm_var s.
End tm_var_handle. (* [@\dadada@] and more *)
(* Assembling STLC.subst_internal when compilation *)
Module subst_internal_410 (STLC: STLC_Interface). 
 Module subst_internal.
 Include tm_var_handle STLC. Include tm_abs_handle STLC.
 Include tm_app_handle STLC. Include tm_unit_handle STLC.
 End subst_internal.
End subst_internal_410.
(* Intermediate Module solely for type checking *)
Module do_tc (STLC: STLC_Interface).
  Include tm_rec_type STLC.
  Parameter (recursor_for_type_checking 
    : __recursor_type_tm_rec).
  Definition term_for_type_checking :=
    recursor_for_type_checking 
      (fun _  ⇒ id → STLC.tm → STLC.tm)
      subst_internal_410.tm_var [@\dadada@] .
End do_tc.
(* Ctx that expose concrete inductive type *)
Module Type ctx_subst_113.
Inductive __internal_tm : Set := [@\dadada@] 
Include subst_internal_410. (* [@\dadada@] and more inclusion *)
End ctx_subst_113.
(* Compilation of recursor, not reusable
    when inductive type extended due to the ctx *)
Module subst_128 (self__STLC: ctx_subst_113).
Include __motive_of_subst_107 self__STLC.
Definition subst :=
  self__STLC.__internal_tm_rec __motiveTsubst
	self__STLC.subst_internal.tm_var [@\dadada@] .
End subst_128.
(* Assembling the whole STLC *)
Module STLC.
Include tm_5. Include tm_prec_72. Include tm_prectm_81.
Include subst_internal_410. Include subst_128.
End v_129.
(* Assembling STLC_bool.subst_internal via reusing 
    most of the former compilation results *)
Module subst_internal_248 (STLC_bool: STLC_Interface).
Include tm_true_197 STLC_bool. Include [@\dadada@]
(* The Reused Compilation result *)
Include tm_var_handle STLC_bool. Include [@\dadada@]
End v_248. 
(* Regenerated FRecursion result *)
Module subst_242 (self__STLC_bool: [@\dadada@]).
Include __motive_of_subst_107 self__STLC_bool.
Definition subst :=
  self__STLC_bool.__internal_tm_rec __motiveTsubst
	self__STLC_bool.subst_internal.tm_var [@\dadada@]
    self__STLC_bool.subst_internal.tm_true [@\dadada@] .
End subst_242. [@\tanc{Cmp-Result-end}@]
\end{lstlisting}
